---
title: "README"
author: "Mikko Virtanen"
date: "19 9 2017"
output: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/stanmodels.R")
source("R/utils.R")
source("R/amomoStan.R")
source("R/flumomoStan.R")
source("R/tools.R")
source("R/datatools.R")
```

## momoStan background

Package to do bayesian version of the EuroMoMo and FluMoMo algorithms [euromomo.eu](http://www.euromomo.eu).

The idea is to extend the models using the [Stan](http://mc-stan.org/) probabilistic programming language. The system is a very flexible tool for doing bayesian analysis. It supports large variety of statistical models, is extensible and has large and active developer aand user communities.

More detailed examples are in the file testing.R. 

## Examples

First load a small dataset

```{r data}
data("fimomodata")
smalldata<-fixMomoData(keep="All")
```

## Simple model

This will take some time:

```{r pressure,echo=FALSE}
amomo<-amomoStan(smalldata,byvar="age",popvar="pop",penalties=c(0,0,1))
```

etc ...
